Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-03-19 Ben_Manuscripts/thesis/intro.tex
comments on intro.

  Although there has been considerable focus on creating membranes with high
  permeabilities, there is a case to be made that shifting the focus to membrane
  selectivity may offer a more effective route towards lowering the cost of 
  membrane separations.~\cite{werber_materials_2016}
  \begin{itemize}
    \item Increasing permeabilities beyond those already achieved may have 
    only a small effect on energy requirements and capital costs. 
    \item Cohen-Tanugi \textit{et al.} calculated that a theoretical tripling of membrane permeability
    would only reduce energy consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
    \item Perhaps the biggest detriment to energy consumption is the practical
	need for multiple membrane passes in order to achieve a desired purity.~\cite{singh_production_2009}
    \item Additionally, many membranes are not suited for high purity separations
    of small neutral species which necessitates chemical and capital costs for
    post-treatment.~\cite{shannon_science_2009,fritzmann_state---art_2007}
%    \item The well-known permeability-selectivity tradeoff, common to dense polymer 
%    membranes, directly correlates an increase in water permeability with an 
%    increase in solute permeability.~\cite{geise_water_2011}
    \item Addressing these problems with highly selective separations may lead to 
    more gains.~\cite{deshmukh_desalination_2015}
 \end{itemize}

@@

  %BJC2: would a figure showing the nanostructures go well here? (a graphene film, a carbon nanotube, a MOF, a zeolite)

  %BJC2: Each tecnhology below will likely have its own heading and be split into 2 or more 
  % paragraphs.
  \textit{Graphene and graphene oxide} Ultrathin-film graphene and graphene oxide membranes
  are an active area of research because they are atomically thick materials and therefore 
  offer potential for extremely high permeability membranes.~\cite{humplik_nanostructured_2011} 
  \begin{itemize}
    \item The tightly packed aromatic network of $sp^2$ hybridized carbon atoms that 
    make up graphene sheets precludes the passage of even the smallest monoatomic species, helium.~\cite{bunch_impermeable_2008}
    \item Controllably-sized pores have been created in pristine graphene by plasma etching
    and by charged particle bombardment.~\cite{surwade_water_2015,russo_atom-by-atom_2012}
    \item Graphene oxide (GO), a highly oxidized modification of graphene, consist of epoxy,
    hydroxyl and carboxylate functional groups.~\cite{hegab_graphene_2015}
    \item Many groups study GO membranes because they have improved antibacterial properties 
    over graphene, leading to less membrane fouling, and because their functionality can be
    modified in order to achieve solute-specific separations.~\cite{liu_antibacterial_2011,he_bioinspired_2013}
    \item Despite their promise, scalable synthesis of monolayer graphene and GO membranes without
    introducing microscopic, performance degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
    \item Multilayered GO membranes have shown considerably more progress since their 
    synthesis procedures are low cost and scalable.~\cite{zhang_size-controlled_2009}
    \item GO sheets are particularly easy to make into multilayered membranes since they 
    stack on top of each other, held together by hydrogen bonds.~\cite{homaeigohar_graphene_2017}
    \item The potential of graphene and GO membrane certainly merits their continued exploration. Many
    groups are still working in order to work on better control and standardization of their synthesis,
    improving their designability for specific separations, and further improving their scalability.~\cite{wei_multilayered_2018}
  \end{itemize}

  \textit{Carbon nanotubes}: Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011}
  \begin{itemize}
    \item CNTs are an allotrope of carbon consisting of tubular graphitic layers.~\cite{iijima_helical_1991}
    \item One can control CNT diameters down to 0.5 nm in size which has inspired the
    creation of CNT membranes for reverse osmosis applications.~\cite{sun_creating_2000}
    \item Molecular dynamics simulations have predicted and experiments have confirmed that
    CNTs are extremely fast transporters of water.~\cite{hummer_water_2001,joseph_why_2008}
    \item MD simulations by Kalra \textit{et al.} predicted water transport at rates comparable
    to the transmembrane protein aquaporin-1.~\cite{kalra_osmotic_2003}
    \item Experiments have exhibited water transport rates orders of magnitude higher than 
    predictions by continuum modeling.~\cite{holt_fast_2006}
    \item This enhancement has been explained as a result of nearly friction-less single-file water
    flow through the hydrophobic CNT interiors.~\cite{kalra_osmotic_2003}
    \item Functionalization of the CNT pore entrances can potentially lead to highly selective separations.~\cite{fornasiero_ion_2008}
	\item Practically, dispersing and aligning CNTs into a polymer matrix is extremely
    difficult because they tend to agglomerate due to van der Waals forces.~\cite{sahoo_polymer_2010}
    \item Some work has been to functionalize the carbon nanotubes in order to better incorporate them,
    however facile incorporation at scale remains a challenge yet to be overcome.~\cite{kim_polysulfone_2007}
  \end{itemize}

@@

  Under the right conditions, the shape and amphiphilic character of liquid 
  crystal monomers drives their self-assembling into ordered nanostructures with
  uniform-sized pores on the order of 1 nm in size.~\cite{gin_polymerized_2008}
  \begin{itemize}
    \item They have been used as membranes before.~\cite{gin_polymerized_2001}
    \item As shown in Figure TBD, monomer 1 will form the inverted hexagonal phase 
    (H\textsubscript{II})~\cite{smith_ordered_1997} while monomer 2 will form the 
    bicontinuous cubic phase (Q\textsubscript{I})~\cite{carter_glycerol-based_2012}
    \item The tails have vinyl groups which can be cross-linked for mechanical strength.
    \item In this work we attempt to understand how one can design LLC membranes as 
    alternative nanostructured materials for highly selective aqueous separations.
    \item We chose to study liquid crystals because they are already suitable as NF 
    membranes and there has been sufficient experimental characterization.~\cite{gin_polymerized_2001,feng_scalable_2014,feng_thin_2016}
  \end{itemize}

@@

  The space group of the Q\textsubscript{I} phase configuration formed by
  monomer 1 is uncertain and thought to be either Pn3m or Ia3d.  %BJC: will have accompanying figure
  \begin{itemize}
    \item 6 Q phase architectures have been identified in small molecule
    amphiphile systems.~\cite{mariani_cubic_1988}
    \item Of these, only 4 are consistent with diffraction data generated
    by the gemini surfactant used here.~\cite{pindzola_cross-linked_2003}
    \item Q$^{230}$ (Ia3d), Q$^{224}$ (Pn3m), Q$^{229}$ (Im3m) or Q$^{212}$ (P4\textsubscript{3}32) phase of type I configuration
    \item The presence of $1 / \sqrt{6}$ and $1 / \sqrt{8}$ peaks rules out the
    Q$^{227}$ (Fd3m) and Q$^{223}$ (Pm3n) configurations.
    \item The Pn3m and Ia3d architectures are the most common~\cite{mariani_cubic_1988,wiesenauer_nanoporous_2012}
    \item The most likely phase is the type I Q$^{230}$ (Ia3d) because it is the
    most common phase observed between lamellar and hexagonal phases and the
    monomeric alkyltrimethylammonium salts used to synthesize the gemini LCs
    exhibit clear Ia3d symmetry.
  \end{itemize}

@@

@@

@@

  Because there is relatively sparse coverage of these types of simulation systems in 
  the literature, we have built a detailed molecular model from the ground up. There 
  are four primary research questions that we will address in this work.
  \begin{enumerate}
    \item What is the nanoscopic structure?
    	\begin{itemize}
    	  \item Before we can try to understand the molecular mechanisms of solute
    	  transport, we need to ensure that we model the chemical environment
    	  within the nanopores in a way that is consistent with experiment.
    	  \item We use experimental structural data in order to validate our model.
    	\end{itemize}
    \item Which solute-membrane interactions have the greatest influence on transport rates?
    	\begin{itemize}
    	  \item After gaining a detailed picture of the nanopore structure, we can 
    	  feel confident that solutes in this system will experience the same 
    	  interactions which are present in a real system.
    	  \item We create independent systems for each of 20 small polar solutes 
    	  and observe transport mechanisms whose dominance is dependent on
    	  solute chemical functionality.
    	  \item We characterize three different trapping mechanisms which lead
    	  to subdiffusive transport behavior.
    	\end{itemize}
    %MRS: maybe talk more about the stochastic modeling itself; for example, could phrase it in terms of
    %how you can test mechanistic models to see if they are consistent with the timeseries, and then how those models
    %can be further extrapolated to physical observables even if the MD simulations cannot. 
    %MRS: this MIGHT include using the effective diffusion in a solution/diffusion model.
    %\item Can we estimate experimentally-relevant macroscopic properties?
    %BJC2: modified thesis
    \item Can we formulate mechanistic models whose dynamical properties are consistent with our
    molecular simulations and can be used to extrapolate macroscopic behavior which MD simulations cannot.
    	\begin{itemize}
    	  \item Using our qualitative understanding of the dominant trapping mechanisms,
    	  we develop stochastic time series models which we can use to mimic solute dynamic
    	  behavior on time scales orders of magnitude longer than our simulations. 
    	  \item We attempt to reproduce both quantitative and qualitative solute trajectory
    	  behavior on MD simulation-length timescales.
    	  \item We then show how we can use our most promsiing model in order to connect 
    	  microscopic transport to macroscopic flux and selectivity.
    	\end{itemize}

@@

  %BJC2: Should I just put title with reference? Or full citation?
  \noindent\textit{Chapter 2}: adapted from manuscript entitled ``Understanding the 
  Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes." 
  published in the Journal of Physical Chemistry B.~\cite{coscia_understanding_2019} \\

>>>>

  Although there has been considerable focus on creating membranes with high
  permeabilities, there is a case to be made that shifting the focus to membrane
  selectivity may offer a more effective route towards lowering the cost of 
  membrane separations.~\cite{werber_materials_2016}
  \begin{itemize}
    \item Increasing permeabilities beyond those already achieved may have 
    only a small effect on energy requirements and capital costs. 
    \item Cohen-Tanugi \textit{et al.} calculated that a theoretical tripling of membrane permeability
    would only reduce energy consumption by up to 15\% in a seawater RO plant.~\cite{cohen-tanugi_quantifying_2014}
%MRS3: detriment -> impediment?
    \item Perhaps the biggest detriment to energy consumption is the practical
	need for multiple membrane passes in order to achieve a desired purity.~\cite{singh_production_2009}
    \item Additionally, many membranes are not suited for high purity separations
    of small neutral species which necessitates chemical and capital costs for
    post-treatment.~\cite{shannon_science_2009,fritzmann_state---art_2007}
%    \item The well-known permeability-selectivity tradeoff, common to dense polymer 
%    membranes, directly correlates an increase in water permeability with an 
%    increase in solute permeability.~\cite{geise_water_2011}
    \item Addressing these problems with highly selective separations may lead to 
    more gains.~\cite{deshmukh_desalination_2015}
 \end{itemize}

@@

  %BJC2: would a figure showing the nanostructures go well here? (a graphene film, a carbon nanotube, a MOF, a zeolite)
  %MRS3: more figures almost always good.

  %BJC2: Each tecnhology below will likely have its own heading and be split into 2 or more 
  % paragraphs.
  \textit{Graphene and graphene oxide}: Ultrathin-film graphene and graphene oxide membranes
  are an active area of research because they are atomically thick materials and therefore 
  offer potential for extremely high permeability membranes.~\cite{humplik_nanostructured_2011} 
  \begin{itemize}
    \item The tightly packed aromatic network of $sp^2$ hybridized carbon atoms that 
    make up graphene sheets precludes the passage of even the smallest monoatomic species, helium.~\cite{bunch_impermeable_2008}
    \item Controllably-sized pores have been created in pristine graphene by plasma etching
    and by charged particle bombardment.~\cite{surwade_water_2015,russo_atom-by-atom_2012}
    \item Graphene oxide (GO), a highly oxidized modification of graphene, consist of epoxy,
    hydroxyl and carboxylate functional groups.~\cite{hegab_graphene_2015}
    \item Many groups study GO membranes because they have improved antibacterial properties 
    over graphene, leading to less membrane fouling, and because their functionality can be
    modified in order to achieve solute-specific separations.~\cite{liu_antibacterial_2011,he_bioinspired_2013}
    \item Despite their promise, scalable synthesis of monolayer graphene and GO membranes without
    introducing microscopic, performance degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
    \item Multilayered GO membranes have shown considerably more progress since their 
    synthesis procedures are low cost and scalable.~\cite{zhang_size-controlled_2009}
    \item GO sheets are particularly easy to make into multilayered membranes since they 
    stack on top of each other, held together by hydrogen bonds.~\cite{homaeigohar_graphene_2017}
    \item The potential of graphene and GO membrane certainly merits their continued exploration. Many
    groups are still working in order to work on better control and standardization of their synthesis,
    improving their designability for specific separations, and further improving their scalability.~\cite{wei_multilayered_2018}
  \end{itemize}

  \textit{Carbon nanotubes}: Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011}
  \begin{itemize}
%MRS3: tubular layers?
    \item CNTs are an allotrope of carbon consisting of tubular graphitic layers.~\cite{iijima_helical_1991}
    \item One can control CNT diameters down to 0.5 nm in size which has inspired the
    creation of CNT membranes for reverse osmosis applications.~\cite{sun_creating_2000}
    \item Molecular dynamics simulations have predicted and experiments have confirmed that
    CNTs are extremely fast transporters of water.~\cite{hummer_water_2001,joseph_why_2008}
    \item MD simulations by Kalra \textit{et al.} predicted water transport at rates comparable
    to the transmembrane protein aquaporin-1.~\cite{kalra_osmotic_2003}
    \item Experiments have exhibited water transport rates orders of magnitude higher than 
    predictions by continuum modeling.~\cite{holt_fast_2006}
    \item This enhancement has been explained as a result of nearly friction-less single-file water
    flow through the hydrophobic CNT interiors.~\cite{kalra_osmotic_2003}
    \item Functionalization of the CNT pore entrances can potentially lead to highly selective separations.~\cite{fornasiero_ion_2008}
	\item Practically, dispersing and aligning CNTs into a polymer matrix is extremely
    difficult because they tend to agglomerate due to van der Waals forces.~\cite{sahoo_polymer_2010}
    \item Some work has been to functionalize the carbon nanotubes in order to better incorporate them,
    however facile incorporation at scale remains a challenge yet to be overcome.~\cite{kim_polysulfone_2007}
  \end{itemize}

@@

  Under the right conditions, the shape and amphiphilic character of liquid 
  crystal monomers drives their self-assembling into ordered nanostructures with
  uniform-sized pores on the order of 1 nm in size.~\cite{gin_polymerized_2008}
  \begin{itemize}
    \item They have been used as membranes before.~\cite{gin_polymerized_2001}
    \item As shown in Figure TBD, monomer 1 will form the inverted hexagonal phase 
    (H\textsubscript{II})~\cite{smith_ordered_1997} while monomer 2 will form the 
    bicontinuous cubic phase (Q\textsubscript{I})~\cite{carter_glycerol-based_2012}
    \item The tails have vinyl groups which can be cross-linked for mechanical strength.
%MRS3: Next bit seems a bit weird. If you making a transition to what you will be studying, it should be higher in indent level, since now you are switching to what you present. But if this is just a brief aside, maybe it should be left out, and then presented later?
    \item In this work we attempt to understand how one can design LLC membranes as 
    alternative nanostructured materials for highly selective aqueous separations.
%MRS3: liquid crystal-based self-assembled nanostructures?  It's the structures that are of interest.
    \item We chose to study liquid crystals because they are already suitable as NF 
    membranes and there has been sufficient experimental characterization.~\cite{gin_polymerized_2001,feng_scalable_2014,feng_thin_2016}
  \end{itemize}

@@

  The space group of the Q\textsubscript{I} phase configuration formed by
  monomer 1 is uncertain and thought to be either Pn3m or Ia3d.  %BJC: will have accompanying figure
  \begin{itemize}
    \item 6 Q phase architectures have been identified in small molecule
    amphiphile systems.~\cite{mariani_cubic_1988}
    \item Of these, only 4 are consistent with diffraction data generated
    by the gemini surfactant used here.~\cite{pindzola_cross-linked_2003}
    \item Q$^{230}$ (Ia3d), Q$^{224}$ (Pn3m), Q$^{229}$ (Im3m) or Q$^{212}$ (P4\textsubscript{3}32) phase of type I configuration
    \item The presence of $1 / \sqrt{6}$ and $1 / \sqrt{8}$ peaks rules out the
    Q$^{227}$ (Fd3m) and Q$^{223}$ (Pm3n) configurations.
    \item The Pn3m and Ia3d architectures are the most common~\cite{mariani_cubic_1988,wiesenauer_nanoporous_2012}
    \item The most likely phase is the type I Q$^{230}$ (Ia3d) because it is the
    most common phase observed between lamellar and hexagonal phases and the
    monomeric alkyltrimethylammonium salts used to synthesize the gemini LCs
    exhibit clear Ia3d symmetry.
%MRS3: is this last bit necessarily implied (symmetry of phasae bby symmetry of salt)?  It's not clear to me it is.
  \end{itemize}

@@

  %MRS3: one issue is that after this paragraph, it's not entirely
  %clear where you are going.  This describes common models, but not
  %how your research is placed in respect to them.

@@

%MRS3: think about if there is a way to better connect the information
%above to the work carried out in the thesis, besides just ``we need a better theory''.

@@

  Because there is relatively sparse coverage of these types of simulation systems in 
  the literature, we have built a detailed molecular model from the ground up. There 
  are four primary research questions that we will address in this work.
  \begin{enumerate}
    \item What is the nanoscopic structure?
    	\begin{itemize}
    	  \item Before we can try to understand the molecular mechanisms of solute
    	  transport, we need to ensure that we model the chemical environment
    	  within the nanopores in a way that is consistent with experiment.
    	  \item We use experimental structural data in order to validate our model.
    	\end{itemize}
    \item Which solute-membrane interactions have the greatest influence on transport rates?
    	\begin{itemize}
    	  \item After gaining a detailed picture of the nanopore structure, we can 
%MRS: below: same, or qualitatively similar, or substantially similar? Think about a bit more. 
    	  feel confident that solutes in this system will experience the same 
    	  interactions which are present in a real system.
    	  \item We create independent systems for each of 20 small polar solutes 
    	  and observe transport mechanisms whose dominance is dependent on
    	  solute chemical functionality.
    	  \item We characterize three different trapping mechanisms which lead
    	  to subdiffusive transport behavior.
    	\end{itemize}
    %MRS: maybe talk more about the stochastic modeling itself; for example, could phrase it in terms of
    %how you can test mechanistic models to see if they are consistent with the timeseries, and then how those models
    %can be further extrapolated to physical observables even if the MD simulations cannot. 
    %MRS: this MIGHT include using the effective diffusion in a solution/diffusion model.
    %\item Can we estimate experimentally-relevant macroscopic properties?
    %BJC2: modified thesis
    \item Can we formulate mechanistic models whose dynamical properties are consistent with our
    molecular simulations and can be used to extrapolate macroscopic behavior which MD simulations cannot.
    	\begin{itemize}
    	  \item Using our qualitative understanding of the dominant trapping mechanisms,
    	  we develop stochastic time series models which we can use to mimic solute dynamic
    	  behavior on time scales orders of magnitude longer than our simulations. 
    	  \item We attempt to reproduce both quantitative and qualitative solute trajectory
    	  behavior on MD simulation-length timescales.
    	  \item We then show how we can use our most promsiing model in order to connect 
    	  microscopic transport to macroscopic flux and selectivity.
    	\end{itemize}

@@

  %MRS: maybe put supporting information for each chapter at the end of the chapter so it's in one place?

  %BJC2: Should I just put title with reference? Or full citation?
  %MRS3: full citation.
  \noindent\textit{Chapter 2}: adapted from manuscript entitled ``Understanding the 
  Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes." 
  published in the Journal of Physical Chemistry B.~\cite{coscia_understanding_2019} \\
